### 2014-11-28 Cuatrimestres/1/TeoriadeControlI/capitulos/12-inobservabilidad.tex
Se elimina mas codigo redundante de diagrmas de bloques

	\begin{figure}
    \centering
    \resizebox{\textwidth}{!}{
        \tikzstyle{block} = [draw, rectangle, minimum height=3em, minimum width=4em]
        \tikzstyle{sum} = [draw, circle]
        \tikzstyle{vecArrow} = [thick, decoration={markings,mark=at position
             1 with {\arrow[semithick]{open triangle 60}}},
             double distance=1.4pt, shorten >= 5.5pt,
             preaction = {decorate},
             postaction = {draw,line width=1.4pt, white,shorten >= 4.5pt}]
        \tikzstyle{innerWhite} = [semithick, white,line width=1.4pt, shorten >= 4.5pt]

>>>>

	\begin{figure}
    \centering
    \resizebox{\textwidth}{!}{
        \tikzstyle{block} = [draw, rectangle, minimum height=3em, minimum width=4em]
